The \dealii Library, Version 9.1

### 2019-06-06 9.1/paper.tex
Update FE_BernardiRaugel summary

\usepackage[normalem]{ulem}

@@

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Denis Davydov,
    Marc Fehling,
    Graham Harper,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Ross Maguire Kynch,
    Matthias Maier,
    Jean-Paul Pelteret,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.1, 2019},
}

@@

\author[4]{Marc~Fehling}
\affil[4]{Institute for Advanced Simulation,
  Forschungszentrum J\"{u}lich GmbH,
  52425 J\"{u}lich, Germany.
  {\texttt{m.fehling@fz-juelich.de}}}

@@

\author[5]{Timo~Heister}
\affil[5]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA
  and Scientific Computing and Imaging Institute,
  72 S Central Campus Drive, Room 3750
  Salt Lake City, UT 84112.
  {\texttt{heister@sci.utah.edu}}}
%
\author[6]{Luca~Heltai}
\affil[6]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265,
  34136, Trieste, Italy.
  {\texttt{luca.heltai@sissa.it}}}

\author[7]{Martin~Kronbichler}
\affil[7]{Institute for Computational Mechanics,
  Technical University of Munich,
  Boltzmannstr.~15, 85748 Garching, Germany.
  {\texttt{kronbichler@lnm.mw.tum.de}}}

\author[8]{Ross~Maguire~Kynch}
\affil[8]{Renishaw Plc,
  Miskin, CF72 8XY, Wales, UK.
  {\texttt{rkynch@gmail.com}}}

\author[9]{Matthias~Maier}
\affil[9]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[3]{Jean-Paul~Pelteret}

@@

\author[10]{David Wells}
\affil[10]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

@@

The major changes of this release are:
%
\begin{itemize}
  \item Improved support for automatic differentiation (see
    Section~\ref{subsec:ad}),
  \item Dedicated support for symbolic algebra (see
    Section~\ref{subsec:sd}),
  \item Full support for $hp$~adaptivity in parallel computations (see
    Section~\ref{subsec:hp}),
  \item Interfaces to the HDF5 file format and libraries (see
    Section~\ref{subsec:hdf5}),
  \item Significantly extended GPU support (see Section~\ref{subsec:gpu}),
  \item Parallel geometric multigrid (GMG) improvements (see
    \cite{ClevengerHeisterKanschatKronbichler2019} and
    Section~\ref{subsec:gmg}),
  \item Four new tutorial programs (step-61, step-62, step-63, step-64),
    as well as one new code gallery program (see
    Section~\ref{subsec:steps}).
\end{itemize}
%
The major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item
  The release contains bug fixes and performance improvements of the
  matrix-free framework and related geometric multigrid solvers. In
  particular, the implementation of the Chebyshev iteration, an often used
  smoother in the matrix-free context, has been revised to reduce vector
  accesses. This speeds up matrix-free multigrid solvers by up to 10-15\%
  on geometries with affine (parallelogram and parallelpiped) cells, and up
  to 5\% on geometries with cells bounded by curved edges and faces.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Full support for $hp$~adaptivity in parallel computations}
\label{subsec:hp}

\dealii{} has had support for $hp$~adaptive methods since around 2005
(documented in \cite{BangerthKayserHerold2007}) and for parallel
computations on distributed meshes since around 2010 (see
\cite{BangerthBursteddeHeisterKronbichler11}), but not for both at the
same time. The challenges to combine these are related to a number of
areas:
\begin{enumerate}
\item Data structures: The data structures necessary to store the
  indices of degrees of freedom are substantially more
  complicated for $hp$~algorithms than for the $h$~adaptive schemes
  that were already implemented. This is because the number of degrees
  of freedom per cell is now no longer constant. Furthermore,
  faces and edges may need to store more than one set of indices if
  the adjacent cells use different polynomial degrees; in the case of
  edges, the number of sets of indices may also be of variable size.

@@

\item Algorithms: Already for $h$~adaptive meshes, enumerating all
  degrees of freedom uniquely on the global mesh is difficult, as evidenced by
  the complications of the algorithms shown in Section 3.1 of
  \cite{BangerthBursteddeHeisterKronbichler11}, which requires more
  than one page of text and is implemented in many hundreds of lines of
  code.

  These difficulties are even more pronounced when using $hp$~adaptivity.
  The main obstacle is the desire to unify the indices of
  matching degrees of freedom on adjacent cells whenever elements with
  continuous polynomials are used. For example, the edge degree of freedom
  of a $Q_2$~element has to be merged with the middle one of the three
  edge degrees of freedom of a $Q_4$~element on a neighboring cell.
  Section 4.2 of \cite{BangerthKayserHerold2007} discusses a sequential algorithm
  that eliminates one of these degrees of freedom in favor of another,
  but it introduces a ``master'' and a ``slave'' side of the
  interface. This is of no major consequence in sequential
  computations, but is inconvenient in parallel computations if the
  ``master'' side is a ghost cell whose degree of freedom indices are
  not (yet) available while enumerating local degrees of freedom, or
  if the master is an artificial cell whose information will never be
  available on a processor.

@@

\item Data transfer patterns: An important algorithm in parallel
  finite element methods is the exchange of information stored on
  cells during mesh repartitioning. This happens, for example, when
  interpolating the solution from one mesh to the next
  adaptively refined mesh; or when adapting the polynomial degrees
  associated with each cell and repartitioning in order to
  balance the computational cost of each processor's partition. When
  using $h$~adaptive methods, the amount of data associated with each
  cell is fixed and the algorithms that implement the data transfer
  are consequently relatively simple. On the other hand, in $hp$~contexts,
  each cell may have a different number of unknowns
  associated with it, and the algorithms that transfer the data are
  substantially more complicated. In order to implement those, we rely
  on recent enhancements of the \pfrst~library (documented in
  \cite{Burstedde2018}) to transfer data of variable size across
  processors. Furthermore, the amount of data associated with each
  cell may be large on cells with higher polynomial degrees, and
  might profit from compression before sending.

\item Balancing computational cost: For $h$~adaptive algorithms, the
  amount of work associated with each cell is essentially the same,
  both during the assembly of linear systems as well as during the
  solver phase. For $hp$~adaptive methods, this is no longer the
  case. Consequently, balancing the cost of work between different
  processors' partitions is no longer as easy as ensuring that every
  processor owns a roughly equal number of cells. Rather, one needs to
  introduce a weighting factor for each cell that describes its
  relative cost compared to some reference. To make things worse, the
  relative cost of assembly on a cell might not match the relative
  cost of the linear solver associated with this cell, leading to
  difficult trade-offs in defining optimal weighting factors. In this
  release, we supplied the basic functionality to attach any amount
  of weighting factors to cells, but users still have to find reasonable
  weights for themselves.
\end{enumerate}

@@

GPU support was significantly extended for the current release:
\begin{itemize}
  \item The \texttt{CUDAWrappers::PreconditionILU} and \texttt{CUDAWrappers::PreconditionIC}
    classes can now be used for preconditioning \texttt{CUDAWrappers::SparseMatrix} objects.
  \item \texttt{LinearAlgebra::distributed::Vector}: the MPI-parallel vector
    class has gained a second template argument \texttt{MemorySpace} which can
    either be \texttt{Host} or \texttt{CUDA}. In the latter case, the data
    resides in GPU memory. By default, the template parameter is
    \texttt{Host} and the behavior is unchanged compared to previous versions.
    When using CUDA, the ghost exchange can be performed either by first copying
    the relevant data to the host, performing MPI communication, and finally
    move the data to the device or, if CUDA-aware MPI is available, by
    performing MPI communication directly between GPUs.
  \item Constrained degrees of freedom: the matrix-free framework now
    supports constrained degrees of freedom. The implementation is based on
    the algorithms described in \cite{ljungkvist2017}. With this addition,
    both Dirichlet boundary conditions and the constraints arising from
    adaptively refined meshes can be imposed within the matrix-free
    framework.
    \textcolor{red}{%
    \sout{The only restriction is that for two-dimensional meshes the
    finite element degree must be odd. There is no such restriction in
    three dimensions.}
    \emph{%
    WB: Can we explain this restriction? It seems odd (pun intended)...
    BT: No, we cannot. I have spent at least two full weeks trying to
    understand why it doesn't work, i.e., gives the wrong result, but I
    don't know. We decided at the time that even with the current
    limitation this was a useful addition.
    MM: I suggest that we then simply not mention the limitation and treat
    it as a known bug. As it is currently worded it can be easily
    interpreted as a fundamental limitation, i.\,e. ``FE with even degree
    are not admissible.''}}

  \item MPI matrix-free computations: using \texttt{LinearAlgebra::distributed::Vector}, the
    matrix-free framework can scale to multiple GPUs by taking
    advantage of MPI. Each MPI process can only use one GPU and therefore, if
    multiple GPUs are available in one node, it is necessary to have as many
    ranks as there are GPUs. Using Nvidia Multi-Process Service (MPS), it is also possible
    for multiple processes to use the same GPU. This can be advantageous if the
    amount of work on one rank is not sufficient to fully utilize a GPU.
\end{itemize}

@@

\textcolor{red}{Missing: performance optimizations, new features, largest
runs now at XYZ (Kronbichler?)}

@@

The original \texttt{\dealii} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{itemize}
 \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019};
 \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
 \item For $hp$~adaptivity: \cite{BangerthKayserHerold2007};
  \item For partition-of-unity (PUM) and enrichment methods of the
    finite element space: \cite{Davydov2016};
 \item For matrix-free and fast assembly techniques:
   \cite{KronbichlerKormann2012,KronbichlerKormann2019};
 \item For computations on lower-dimensional manifolds:
   \cite{DeSimoneHeltaiManigrasso2009};
 \item For integration with CAD files and tools:
   \cite{HeltaiMola2015};
 \item For Boundary Elements Computations:
   \cite{GiulianiMolaHeltai-2018-a};
 \item For \texttt{LinearOperator} and \texttt{PackagedOperation} facilities:
   \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b}.
 \item For uses of the \texttt{WorkStream} interface:
   \cite{TKB16};
   \item For uses of the \texttt{ParameterAcceptor} concept, the
     \texttt{MeshWorker::ScratchData} base class, and the
     \texttt{ParsedConvergenceTable} class: \cite{SartoriGiulianiBardelloni-2018-a}.
\end{itemize}

\marginpar{I'm sure we have new interfaces. HDF5 and the various AD/SD
  libraries come to mind. Please update. MM: The list actually looks pretty
  complete (I have not verified that we actually cite *all* canonical
  publications for a given library).}
\dealii can interface with many other libraries:
\begin{multicols}{3}
\begin{itemize}
\item ADOL-C \cite{Griewank1996a,adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS and LAPACK \cite{lapack}
\item cuSOLVER \cite{cusolver}
\item cuSPARSE \cite{cusparse}
\item Gmsh \cite{geuzaine2009gmsh}
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{Burstedde2018,p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item ROL \cite{ridzal2014rapid}
\item ScaLAPACK \cite{slug}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item TBB \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

@@

\dealii is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
% updated 6/05/2019
  Giovanni Alzetta,
  Mathias Anselmann,
  Daniel Appel,
  Alexander Blank,
  Vishal Boddu,
  Benjamin Brands,
  Pi-Yueh Chuang,
  T. Conrad Clevenger,
  Sambit Das,
  Stefano Dominici,
  Nivesh Dommaraju,
  Niklas Fehn,
  Isuru Fernando,
  Andreas Fink,
  Daniel Garcia-Sanchez,
  Rene Gassm{\"o}ller,
  Alexander Grayver,
  Joshua Hanophy,
  Logan Harbour,
  Daniel Jodlbauer,
  Stefan Kaessmair,
  Eldar Khattatov,
  Alexander Knieps,
  Uwe K{\"o}cher,
  Kurt Kremitzki,
  Dustin Kumor,
  Damien Lebrun-Grandie,
  Jonathan Matthews,
  Stefan Meggendorfer,
  Pratik Nayak,
  Lei Qiao,
  Ce Qin,
  Reza Rastak,
  Roland Richter,
  Alberto Sartori,
  Svenja Schoeder,
  Sebastian Stark,
  Antoni Vidal,
  Jiaxin Wang,
  Yuxiang Wang,
  Zhuoran Wang.

>>>>

@@

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Denis Davydov,
    Graham Harper
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Ross Maguire Kynch,
    Matthias Maier,
    Jean-Paul Pelteret,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.1, 2019},
}

@@

@@

\author[4]{Timo~Heister}
\affil[4]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA
  and Scientific Computing and Imaging Institute,
  72 S Central Campus Drive, Room 3750
  Salt Lake City, UT 84112.
  {\texttt{heister@sci.utah.edu}}}
%
\author[5]{Luca~Heltai}
\affil[5]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265,
  34136, Trieste, Italy.
  {\texttt{luca.heltai@sissa.it}}}

\author[6]{Martin~Kronbichler}
\affil[6]{Institute for Computational Mechanics,
  Technical University of Munich,
  Boltzmannstr.~15, 85748 Garching, Germany.
  {\texttt{kronbichler@lnm.mw.tum.de}}}

\author[7]{Ross~Maguire~Kynch}
\affil[7]{Renishaw Plc,
  Miskin, CF72 8XY, Wales, UK.
  {\texttt{rkynch@gmail.com}}}

\author[8]{Matthias~Maier}
\affil[8]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[4]{Jean-Paul~Pelteret}

@@

\author[9]{David Wells}
\affil[9]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

@@

The major changes of this release are:
%
\begin{itemize}
  \item Improved support for automatic differentiation (see
    Section~\ref{subsec:ad}),
  \item Dedicated support for symbolic algebra (see
    Section~\ref{subsec:sd}),
  \item Full support for $hp$ adaptivity in parallel computations (see
    Section~\ref{subsec:hp}),
  \item Interfaces to the HDF5 file format and libraries (see
    Section~\ref{subsec:hdf5}),
  \item Significantly extended GPU support (see Section~\ref{subsec:gpu}),
  \item Parallel geometric multigrid (GMG) improvements (see
    \cite{ClevengerHeisterKanschatKronbichler2019} and
    Section~\ref{subsec:gmg}),
  \item Four new tutorial programs (step-61, step-62, step-63, step-64),
    as well as one new code gallery program (see
    Section~\ref{subsec:steps}).
\end{itemize}
%
The major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item
  The release contains bug fixes and performance improvements of the
  matrix-free framework and related geometric multigrid solvers. In
  particular, the implementation of the Chebyshev iteration, an often used
  smoother in the matrix-free context, has been revised to reduce vector
  accesses. This speeds up matrix-free multigrid solvers by up to 10-15\%
  on geometries with affine (parallelogram and parallelpiped) cells, and up
  to 5\% on geometries with cells bounded by curved edges and faces.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Full support for $hp$ adaptivity in parallel computations}
\label{subsec:hp}

\dealii{} has had support for $hp$ adaptive methods since around 2005
(documented in \cite{BangerthKayserHerold2007}) and for parallel
computations on distributed meshes since around 2010 (see
\cite{BangerthBursteddeHeisterKronbichler11}), but not for both at the
same time. The challenges to combine these are related to a number of
areas:
\begin{enumerate}
\item Data structures: The data structures necessary to store the
  indices of degrees of freedom are necessarily substantially more
  complicated for $hp$ algorithms than for the $h$-adaptive schemes
  that were already implemented. This is because the number of degrees
  of freedom per cell is now no longer constant. Furthermore,
  faces and edges may need to store more than one set of indices if
  the adjacent cells use different polynomial degrees; in the case of
  edges, the number of sets of indices may also be of variable size.

@@

\item Algorithms: Already for $h$ adaptive meshes, enumerating all
  degrees of freedom on the global mesh is difficult, as evidenced by
  the complications of the algorithms shown in Section 3.1 of
  \cite{BangerthBursteddeHeisterKronbichler11}, which requires more
  than one page of text and is implemented in many hundreds of lines of
  code.

  These difficulties are even more pronounced when using $hp$
  adaptivity. The main obstacle is the desire to unify the indices of
  matching degrees of freedom on adjacent cells, such as the edge
  degree of freedom of a $Q_2$ element with the middle one of
  the three edge degrees of freedom of a $Q_4$ element on a
  neighboring cell. Section 4.2 of
  \cite{BangerthKayserHerold2007} discusses a sequential algorithm
  that eliminates one of these degrees of freedom in favor of another,
  but it introduces a ``master'' and a ``slave'' side of the
  interface. This is of no major consequence in sequential
  computations, but is inconvenient in parallel computations if the
  ``master'' side is a ghost cell whose degree of freedom indices are
  not (yet) available while enumerating local degrees of freedom, or
  if the master is an artificial cell whose information will never be
  available on a processor.

@@

\item Data transfer patterns: An important algorithm in parallel
  finite element methods is the exchange of information stored on
  cells during mesh repartitioning. This happens, for example, when
  interpolating the solution from one mesh to the next,
  adaptively-refined mesh; or when adapting the polynomial degrees
  associated with each cell and repartitioning in order to
  balance the computational cost of each processor's partition. When
  using $h$ adaptive methods, the amount of data associated with each
  cell is fixed and the algorithms that implement the data transfer
  are consequently relatively simple. On the other hand, in $hp$
  contexts, each cell may have a different number of unknowns
  associated with it, and the algorithms that transfer the data are
  substantially more complicated. Furthermore, the amount of data
  associated with each cell may be large on cells with higher
  polynomial degrees, and might profit from compression before
  sending.

\item Balancing computational cost: For $h$-adaptive algorithms, the
  amount of work associated with each cell is essentially the same,
  both during the assembly of linear systems as well as during the
  solver phase. For $hp$-adaptive methods, this is no longer the
  case. Consequently, balancing the cost of work between different
  processors' partitions is no longer as easy as ensuring that every
  processor owns a roughly equal number of cells. Rather, one needs to
  introduce a weighting factor for each cell that describes its
  relative cost compared to some reference. To make things worse, the
  relative cost of assembly on a cell might not match the relative
  cost of the linear solver associated with this cell, leading to
  difficult trade-offs in defining optimal weighting factors.
\end{enumerate}

@@

GPU support was significantly extended for the current release:
\begin{itemize}
  \item The \texttt{CUDAWrappers::PreconditionILU} and \texttt{CUDAWrappers::PreconditionIC}
    classes can now be used for preconditioning \texttt{CUDAWrappers::SparseMatrix} objects.
  \item \texttt{LinearAlgebra::distributed::Vector}: the MPI-parallel vector
    class has gained a second template argument \texttt{MemorySpace} which can
    either be \texttt{Host} or \texttt{CUDA}. In the latter case, the data
    resides in GPU memory. By default, the template parameter is
    \texttt{Host} and the behavior is unchanged compared to previous versions.
    When using CUDA, the ghost exchange can be performed either by first copying
    the relevant data to the host, performing MPI communication, and finally
    move the data to the device or, if CUDA-aware MPI is available, by
    performing MPI communication directly between GPUs.
  \item Constrained degrees of freedom: the matrix-free framework now
    supports constrained degrees of freedom. The implementation is based on the algorithms described in
    \cite{ljungkvist2017}. With this addition, both Dirichlet
    boundary conditions and the constraints arising from adaptively
    refined meshes can be imposed within the matrix-free framework. The only restriction is that for two-dimensional meshes the
    finite element degree must be odd.  
    \marginpar{Can we explain this restriction? It seems odd (pun intended)...}
    \marginpar{BT: No, we cannot. I have spent at least two full weeks trying to
    understand why it doesn't work, i.e., gives the wrong result, but I don't know. We decided at the time that
    even with the current limitation this was a useful addition.}
    There is no such restriction in three
    dimensions.
  \item MPI matrix-free computations: using \texttt{LinearAlgebra::distributed::Vector}, the
    matrix-free framework can scale to multiple GPUs by taking
    advantage of MPI. Each MPI process can only use one GPU and therefore, if
    multiple GPUs are available in one node, it is necessary to have as many
    ranks as there are GPUs. Using Nvidia Multi-Process Service (MPS), it is also possible
    for multiple processes to use the same GPU. This can be advantageous if the
    amount of work on one rank is not sufficient to fully utilize a GPU.
\end{itemize}

@@

\marginpar{Missing: performance optimizations, new features,
largest runs now at XYZ (Kronbichler?)}

@@

The original \texttt{\dealii} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{itemize}
 \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019};
 \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
 \item For $hp$ adaptivity: \cite{BangerthKayserHerold2007};
  \item For partition-of-unity (PUM) and enrichment methods of the
    finite element space: \cite{Davydov2016};
 \item For matrix-free and fast assembly techniques:
   \cite{KronbichlerKormann2012,KronbichlerKormann2019};
 \item For computations on lower-dimensional manifolds:
   \cite{DeSimoneHeltaiManigrasso2009};
 \item For integration with CAD files and tools:
   \cite{HeltaiMola2015};
 \item For Boundary Elements Computations:
   \cite{GiulianiMolaHeltai-2018-a};
 \item For \texttt{LinearOperator} and \texttt{PackagedOperation} facilities:
   \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b}.
 \item For uses of the \texttt{WorkStream} interface:
   \cite{TKB16};
   \item For uses of the \texttt{ParameterAcceptor} concept, the
     \texttt{MeshWorker::ScratchData} base class, and the
     \texttt{ParsedConvergenceTable} class: \cite{SartoriGiulianiBardelloni-2018-a}.
\end{itemize}

\marginpar{I'm sure we have new interfaces. HDF5 and the various AD/SD
  libraries come to mind. Please update.}
\dealii can interface with many other libraries:
\begin{multicols}{3}
\begin{itemize}
\item ADOL-C \cite{Griewank1996a,adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS and LAPACK \cite{lapack}
\item cuSOLVER \cite{cusolver}
\item cuSPARSE \cite{cusparse}
\item Gmsh \cite{geuzaine2009gmsh}
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item ROL \cite{ridzal2014rapid}
\item ScaLAPACK \cite{slug}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item TBB \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

@@

\dealii is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people contributed code to
this release:\\
%
% get this from the changes/*/* files using the command listed in the
% release-tasks paper and remove the authors of this paper
%
% updated 5/12/2019
\marginpar{Remove all other authors of this paper}
\marginpar{Do we want to spell out who the Gingko devs are?}
  Giovanni Alzetta,
  Mathias Anselmann,
  Daniel Appel,
  Alexander Blank,
  Vishal Boddu,
  Benjamin Brands,
  Pi-Yueh Chuang,
  T. Conrad Clevenger,
  Sambit Das,
  the Ginkgo developers,
  Stefano Dominici,
  Nivesh Dommaraju,
  Marc Fehling,
  Niklas Fehn,
  Isuru Fernando,
  Andreas Fink,
  Daniel Garcia-Sanchez,
  Rene Gassm{\"o}ller,
  Alexander Grayver,
  Joshua Hanophy,
  Logan Harbour,
  Graham Harper,
  Daniel Jodlbauer,
  Stefan Kaessmair,
  Eldar Khattatov,
  Alexander Knieps,
  Uwe K{\"o}cher,
  Kurt Kremitzki,
  Dustin Kumor,
  Ross Kynch,
  Damien Lebrun-Grandie,
  Jonathan Matthews,
  Stefan Meggendorfer,
  Pratik Nayak,
  Lei Qiao,
  Ce Qin,
  Reza Rastak,
  Roland Richter,
  Alberto Sartori,
  Svenja Schoeder,
  Sebastian Stark,
  Antoni Vidal,
  Jiaxin Wang,
  Yuxiang Wang,
  Zhuoran Wang.
